---
title: "SSF simulation all birds"
author: "Luis Antonio Arias Medellin"
date: "August 13, 2019"
output: html_document
---

#MULTIPLE BIRDS

## FORMAT DATA BASE FOR ANALYSIS

http://tlocoh.r-forge.r-project.org/tips/isopleth_overlap_auto.html

## Load required packages

```{r, include=FALSE}
#Load libraries
library("openxlsx")
library("NISTunits")
library("rgdal")
library("ggmap")
library("SDMTools")
library("raster")
library("MetaLandSim") # need to run code source("https://bioconductor.org/biocLite.R") biocLite("Biobase")
library("rgeos")
library("maps")
library("maptools")
library("geosphere")
library("amt")
library("tidyr")
library("cowplot")
library("reshape2")
library("dplyr")
library("ggplot2")
library("ggrepel")
library("GGally")
library("parallel")
```

#Prepare GPS data

```{r, include=FALSE}
#Remove anything on workspace
rm(list=ls(all=TRUE))

#Source functions
source("Clean SSF data base.R") #I just dpulicated the code I used for cleaning the tleemtry data just in case I modified the latter, so to avoid that the changes affect the present code 

#Fuction for cleaning telemetry data base
clean.tel.data()

#Copy data base
original.database<-prueba

#Select only columns of interest
original.database<-original.database[,c("LOCATION.X","LOCATION.Y","TIME","FREQ")]

#Rename columns
colnames(original.database)<-c("x","y","t","id")

#Number of GPS points per individual
original.database %>%
  group_by(id) %>% 
  summarise(num.obs=n()) %>% 
  ungroup() %>% 
  arrange(desc(num.obs))

#Remove elements that I will not use
rm(clean.freq,clean.tel.data,prueba,m)
```

#Prepare map

```{r}
#Load raster
land_use_raster<-raster("Map layers/Aug27_15rasters/forest27")

#Make a matrix to reclsify values from 1 to 1 and the new value is 0
m<-matrix(c(0,1,0,
            1,2,1),ncol=3,byrow=T) 

#Reclassify values
land_use_raster<-reclassify(land_use_raster,m)
names(land_use_raster) <- "forest27"

rm(m)
```

#Prepare information that will have the frequency of each individual, the patch were it was captured and the information of each patch where the individual was captured

```{r}
#Read excel data base of patch id, patch size and % forest
patches.info<-read.xlsx("Data bases/Information patches Costa Rica.xlsx",sheet=1)
freq.patches<-read.xlsx("Data bases/Frequencies patches.xlsx",sheet=1)

#Keep columns of interest
patches.info<-patches.info[,c("PATCH_ID","PERCENT_FOREST","ELEVATION","Psize")]

#Rename columns
colnames(patches.info)<-c("Patch","percent_forest","elevation","patch_size") #****There is no information on patch 15, 27, 28, 35, 62, 63. Patches 12 and 39 are on the database but there is no information since they have NA

```


```{r}
#Create a data frame with id as the first column and the second column has a data frame inside it with the x,y and time (t)
condensed.dataframe <- original.database %>% nest(-id)

#Show the frequency of the birds I followed
unique(condensed.dataframe$id)

#Subset certain individuals since I cannot run the code with certain frequencies. ****CHECK LATER HOW TO RUN THE CODE WITH ALL FREQUENCIES
condensed.dataframe.subset<-subset(condensed.dataframe,condensed.dataframe$id==232 |
                  condensed.dataframe$id==881 |
                  condensed.dataframe$id==942 |
                  condensed.dataframe$id==312 |
                  condensed.dataframe$id==171 |
                  condensed.dataframe$id==352 |
                  condensed.dataframe$id==511 |
                  condensed.dataframe$id==551 |
                  condensed.dataframe$id==731 |
                  condensed.dataframe$id==760 |
                  condensed.dataframe$id==851 |
                  condensed.dataframe$id==881 |
                  condensed.dataframe$id==973 |
                  condensed.dataframe$id==392 |
                  condensed.dataframe$id==202) 

#dat_all_original$id==472
#dat_all_original$id==910
#dat_all_original$id==821
#dat_all_original$id==791
#dat_all_original$id==702
#dat_all_original$id==672
#dat_all_original$id==631
#dat_all_original$id==591                 
#dat_all_original$id==273) #Just added this one
#dat_all_original$id==432) #Just added this one
#432 only moved in forested area, so the interaction terms of step length and habitat selection between habitats is not working since there are no steps in the matrix
#273 has only 4 movments in the forest, so the interaction is not working
#591 only moved in MATRIX area, so the interaction terms of step length and habitat selection between habitats is not working since there are no steps in the FOREST
#631 MOSTLY moved in MATRIX area, so the interaction terms of step length and habitat selection between habitats is not working since there IS 1 step in the FOREST
#672 MOSTLY moved in MATRIX area, so the interaction terms of step length and habitat selection between habitats is not working since there IS 0 step in the FOREST
#702 MOSTLY moved in MATRIX area, so the interaction terms of step length and habitat selection between habitats is not working since there IS 0 step in the FOREST
#791 MOSTLY moved in MATRIX area, so the interaction terms of step length and habitat selection between habitats is not working since there IS 0 step in the FOREST
#821 MOSTLY moved in forest area, so the interaction terms of step length and habitat selection between habitats is not working since there IS 0 step in the matrix
#910 MOSTLY moved in MATRIX area, so the interaction terms of step length and habitat selection between habitats is not working since there IS 0 step in the FOREST
#472 is giving me a very unsual value of the parameter and I do not know why

#273, 352,511 472, 591, 672, 702, 791, 821, 973, 202 cannot fit model
#312, 171,731, 760, 392, 631, 851 give NA or INF values on estimate or confidence intervals
```

```{r}
#Make a track for each individual
condensed.dataframe.subset <- condensed.dataframe.subset %>%
mutate(trk = lapply(data, function(d) {
mk_track(d, x, y, t )
}))
```

```{r}
#Summarize sampling rate of all individuals
condensed.dataframe.subset %>% mutate(sr = lapply(trk, summarize_sampling_rate)) %>%
select(id, sr) %>% unnest
```

#Make tracks
```{r}


condensed.dataframe.subset <- condensed.dataframe.subset %>% mutate(ssf = lapply(trk, function(x) {
x %>% 
    track_resample(rate = minutes(5), tolerance = minutes(2)) %>% #A track will be considered if the two consecutive GPS points are separated by 5 minutes +- 2 minutes of tolerance
    filter_min_n_burst(min_n = 3) %>% #Keep only tracks that have three consecutive locations, which is the minimum requeried for doing the analysis
    steps_by_burst() %>% #Converts the points to tracks
    random_steps() %>% #Makes 9 random steps
    extract_covariates(land_use_raster, where = "both") %>% #Extracts covariates of vegetation on initial and ending location. In "amt tutorial.pdf" it explains the following: covariate values at the start and the end of a step can also be included in the model as interaction with each other, to test hypotheses of the type: Are animals more likely to stay in a given habitat, if they are already in the habitat?
    mutate(forest27_start = factor(forest27_start, levels = c(0, 1), labels = c("matrix", "forest"))) %>% #factor (forest27_start you have to check the name of the column of the data base that is generated one step before (in this case is forest27_start). Just run the 2 precedent pipe lines and a tibble with the names of the column will appeaar)
    mutate(forest27_end = factor(forest27_end, levels = c(0, 1), labels = c("matrix", "forest"))) %>% 
    mutate(log_sl_ = log(sl_)) #Obtain logarithm of step lenght
}))

```

#Plot habitat selection by bird (includes all birds)
```{r}
#Obtain the information from the condensed data frame
tracking.database.unlisted<- condensed.dataframe.subset %>% 
  select(id, ssf) %>% 
  unnest %>%
  select(id,case_,step_id_,sl_,ta_,forest27_start,forest27_end,log_sl_) %>% 
  filter(case_==TRUE) %>% 
  ungroup()


counts<-table(tracking.database.unlisted$forest27_end,tracking.database.unlisted$id)
par(mar=c(5,5,2,9),xpd=T)
barplot(counts,xlab="Bird id",ylab="Proportion of GPS points per habitat",col=c("grey50","grey"),las=2)

legend("topright",legend=c("Non-forested area","Forested area"),fill=c("grey","grey50"),bty="n")

counts<-data.frame(prop.table(t(counts),margin=1))

counts<-cbind(counts[1:(nrow(counts)/2),c("Var1","Freq")],counts[((nrow(counts)/2)+1):nrow(counts),"Freq"]) 
colnames(counts)<-c("freq","matrix","forest")
counts<-counts[order(-counts$matrix),]
counts.matrix<-t(data.matrix(counts[,c("matrix","forest")]))
colnames(counts.matrix)<-counts[,1]

#jpeg("Graphs/forest end by id frequency.jpg",quality=100,width=1000,height=700)
##**FOR THE FORESTED AREA, A LOT OF FREQUENCIES DO NOT HAVE OBSERVATION. IN ADDITION, THE PROPORTION OF 
par(mar=c(5,5,2,9),xpd=T)
barplot(counts.matrix,xlab="Bird id",ylab="Proportion of GPS points per habitat",col=c("grey","grey50"),las=2)

legend(x=17,y=0.8,legend=c("Non-forested area","Forested area"),fill=c("grey","grey50"),bty="n")


#dev.off()



#Step length by bird
tracking.database.unlisted %>% 
  mutate(id=as.factor(id)) %>% 
  ggplot(aes(x=id,y=log_sl_)) +
  geom_boxplot() +
  xlab("Bird id") +
  ylab("Log step length")
#ggsave("Graphs/Step length by bird.jpg")


#Turning angle by bird
tracking.database.unlisted %>% 
  mutate(id=as.factor(id)) %>% 
  ggplot(aes(x=id,y=ta_)) +
  geom_boxplot() +
  xlab("Bird id") +
  ylab("Turning angle") +
  geom_hline(yintercept=c(-180,180),linetype="dashed")
#ggsave("Graphs/Turning angle by bird.jpg")

 
rm(counts,counts.matrix)
```

#LM for differences between step length in patches

```{r}
#Merge variables of movement behavior with environmental variables of patches. #**Although now that I think about it, it would be better to have the environmental variables of a buffer of each step
tracking.database.unlisted<-freq.patches %>% 
  inner_join(tracking.database.unlisted,by=c("FREQ"="id")) %>% 
  inner_join(patches.info,by=c("PATCH"="Patch")) %>% 
  mutate(logpatch_size=log(patch_size)) %>% 
  select(FREQ,log_sl_,logpatch_size,percent_forest,elevation) 

tracking.database.unlisted %>% 
  ggpairs(upper=list(continuous="points"),lower=list(continuous="cor"))


library("nlme")
#Model without random structure
mod.1<-gls(log_sl_ ~logpatch_size+percent_forest+elevation,method = "REML", data = d)
summary(mod.1)


#GLMM nesting frequency
mod.2<-lme(log_sl_~logpatch_size+percent_forest+elevation,random = ~1 | FREQ,data=d,method="REML")
summary(mod.2)

#without patch size
mod.3<-lme(log_sl_~percent_forest+elevation,random = ~1 | FREQ,data=d,method="REML")
summary(mod.3)

#Without percent of forest
mod.4<-lme(log_sl_~elevation,random = ~1 | FREQ,data=d,method="REML")
summary(mod.4)

library("MuMIn")
Weights(AIC(mod.1,mod.2,mod.3,mod.4))

tracking.database.unlisted %>% 
  ggplot(aes(x=elevation,y=log_sl_)) +
  geom_point() + 
  geom_smooth(method="lm",col="red")
```



#Fit models
```{r}
#This was the original model, which used log_sl and sl in the same model. The authors did it that way, although it is weird that two variables that are transformed are used in the same model. I will use only one of them to fit the model
#m2 <- m2 %>% mutate(fit = map(ssf, ~ fit_issf(.,case_ ~ forest27_end + log_sl_ + sl_  + log_sl_:forest27_end + sl_:forest27_end + strata(step_id_))))

condensed.dataframe.subset <- condensed.dataframe.subset %>% 
  mutate(fit = map(ssf, ~ fit_issf(.,case_ ~ forest27_end + log_sl_ + ta_  + log_sl_:forest27_end + ta_:forest27_end + strata(step_id_))))


#Make a data base with the values of each parameter. 
parameters.simulations <- data.frame(num.simulation=condensed.dataframe.subset$id) #*** IN THIS LINE I WOULD PUT THE NUMBER OF SIMULATIONS I WOULD LIKE TO DO, BUT NO I AM PUTTING THE ID OF THE BIRD SINCE EACH ONE HAS A SPECIFIC PARAMTER

for (i in 1:nrow(condensed.dataframe.subset)) {
  
  parameters.simulations$shape.step.length[[i]] <- sl_shape(condensed.dataframe.subset$fit[[i]])  #It uses a gamma distribution for step length. I think this is the mean. ***Understand why are they using a gamma distribution. HERE ALSO I WILL PUT THE DIFFERENT VALUES FOR THE GAMMA DISTRIBUTION I WOULD LIKE TO SIMULATE
  
  parameters.simulations$scale.step.length[[i]] <- sl_scale(condensed.dataframe.subset$fit[[i]]) #It uses a gamma distribution for step length. I think this is the scale, which is part of what will determine the distribution ***Understand why are they using a gamma distribution. HERE ALSO I WILL PUT THE DIFFERENT VALUES FOR THE GAMMA DISTRIBUTION I WOULD LIKE TO SIMULATE

  
  parameters.simulations$habitat.utilization[[i]] <- coef(condensed.dataframe.subset$fit[[i]])["forest27_endforest"] #***HERE ALSO I WILL PUT THE DIFFERENT VALUES FOR THE HABITAT SELECTION COEFFICIENT I WOULD LIKE TO SIMULATE
  
}

#Make a splitted list with the id. of the simulation number
#parameters.simulations<-split(parameters.simulations,parameters.simulations$num.simulation)





#I will make a list of the patches where the birds will be moving. ###***HERE I CAN MODIFY THE CODE SO THAT I CAN PUT ANY PATCH I WANT. FOR NOW I AM USING PATCHES WERE THE BIRDS WERE CAPTURED
#Make a list with the forest raster cropped to the extent of the animal that moved
structure <- list(id.freq=numeric(),forest.raster.cropped=list())

#Make a splitted list with the id. freq
forest.raster.cropped<-split(condensed.dataframe.subset$id,condensed.dataframe.subset$id)

#Construct the list with the elements
for (i in 1:length(forest.raster.cropped)){
  
  #Copy the structure of the list I want
  forest.raster.cropped[[i]] <- structure
  
  #Put the id. freq
  forest.raster.cropped[[i]]$id.freq <- condensed.dataframe.subset$id[[i]] #***HERE INSTEAD OF PUTTING THIS ID FREQUENCY I WOULD PUT THE PATCH CHARACTERISTICS
  
  #Crop the map to the area in which the animal moved. #****HERE I WOULD PUT ANY CROPPED MAP
  forest.raster.cropped[[i]]$forest.raster.cropped <- crop(land_use_raster, amt::bbox(condensed.dataframe.subset$trk[[i]], spatial = TRUE, buff = 1e3))
  
  #Store movment kernel
  #forest.raster.cropped[[i]]$movement.kernel <- movement_kernel(parameters.simulations$scale.step.length[[i]], parameters.simulations$shape.step.length[[i]], forest.raster.cropped[[i]]$forest.raster.cropped)
  
  #Store habitat kernel
  #forest.raster.cropped[[i]]$habitat.kernel <- habitat_kernel(list(forest27 = parameters.simulations$habitat.kernel[[i]]), forest.raster.cropped[[i]]$forest.raster.cropped)
  
  #Sotre forest raster labaled. #****HERE I WOULD PUT ANY CROPPED MAP
  forest.raster.cropped[[i]]$forest.raster.cropped.labeled<-ConnCompLabel(forest.raster.cropped[[i]]$forest.raster.cropped)
  
}




#This chunk is for obtaining the coordinates of the focal patch from Adam's data base and then figuring out the patch id in the croppped labeled map
#Import data base with information about patches and xy locations of the patch
patches.locations<-read.xlsx("Data bases/Information patches Costa Rica.xlsx",sheet=1)

#Select columns with patch and coordinates information
patches.locations<-patches.locations[,c("PATCH_ID","X","Y")]

#Import data base with information about frequencies with patches
frequencies.patches<-read.xlsx("Data bases/Frequencies patches.xlsx",sheet=1)

#MErge the patches where birds were sampled with xy information
frequencies.patches<-merge(frequencies.patches,patches.locations,by.x="PATCH",by.y="PATCH_ID",all=T)

#Remove data base
rm(patches.locations)

#I will add the information of the patches I will simulate. ***FOR NOW I WILL DO THE PATCHES WHERE THE BIRDS WERE CAPTURED, BUT I CAN DO ANY PATCH

#Make a list
structure <- list(id.freq=numeric(),focal.patch=list())

#Make a splitted list with the id. freq
results.simulations <- focal.patch.database<-split(condensed.dataframe.subset$id,condensed.dataframe.subset$id)


#I will obtain the cell number form the coordinate of the patch where the bird was captured
for (i in 1:length(focal.patch.database)){
  
  #Copy the structure of the list I want
  focal.patch.database[[i]] <- structure
  
  focal.patch.database[[i]]$id.freq <- condensed.dataframe.subset$id[[i]] #***HERE INSTEAD OF PUTTING THIS ID FREQUENCY I WOULD PUT THE PATCH CHARACTERISTICS
  
  #Obtain the x y values of the focal patch
  focal.patch.database[[i]]$focal.patch.xy <- subset(frequencies.patches,frequencies.patches$FREQ==focal.patch.database[[i]]$id.freq)[,c("X","Y")]
  
  #Obtain the cell number from the xy cordinate
  focal.patch.database[[i]]$focal.patch.label <- forest.raster.cropped[[i]]$forest.raster.cropped.labeled [cellFromXY (forest.raster.cropped[[i]]$forest.raster.cropped.labeled, focal.patch.database[[i]]$focal.patch.xy)]
  
}

rm(structure)
```

### Plot

```{r}

#Obtain the parameters with their confidence internvals
graph.parameters.database <- condensed.dataframe.subset %>% mutate(coef = map(fit, ~ broom::tidy(.x$model))) %>%
select(id, coef) %>% unnest %>%
mutate(id = factor(id),
       term=if_else(term=="forest27_endforest","Habitat selection",term),
       term=if_else(term=="log_sl_","Log step length",term),
       term=if_else(term=="ta_","Turning angle",term),
       term=if_else(term=="forest27_endforest:log_sl_","Log step length by habitat",term),
       term=if_else(term=="forest27_endforest:ta_","Turning angle by habitat",term)) %>% group_by(term) %>%
summarize(
mean = mean(estimate),
ymin = mean - 1.96 * sd(estimate),
ymax = mean + 1.96 * sd(estimate)
)

graph.parameters.database$x <- 1:nrow(graph.parameters.database)
data <- condensed.dataframe.subset %>% mutate(coef = map(fit, ~ broom::tidy(.x$model))) %>%
select(id, coef) %>% unnest %>% 
mutate(id = factor(id)) #filter(conf.low!=-Inf)  %>% #I added this line since there are -inf values on the data set 

#Plot small version of the plot
data %>% 
  mutate(term=if_else(term=="forest27_endforest","Habitat selection",term),
         term=if_else(term=="log_sl_","Log step length",term),
         term=if_else(term=="ta_","Turning angle",term),
         term=if_else(term=="forest27_endforest:log_sl_","Log step length by habitat",term),
         term=if_else(term=="forest27_endforest:ta_","Turning angle by habitat",term)) %>% 
  ggplot(., aes(x = term, y = estimate, group = id, col = id)) +
# geom_rect(mapping = aes(xmin = x - .4, xmax = x + .4, ymin = ymin,
# ymax = ymax, y = mean), data = d2 %>% mutate(x = as.numeric(x)), inherit.aes = FALSE,
# fill = "grey90") +
geom_pointrange(aes(ymin = conf.low, ymax = conf.high),
position = position_dodge(width = 0.7), size = 0.8)  +
  geom_errorbar(data = graph.parameters.database, aes(x = term, y = mean, ymin = mean, ymax = mean), inherit.aes = FALSE,
size = 1) +
geom_hline(yintercept = 0, lty = 2) +
labs(x = "Parameters", y = "Relative Selection Strength") +
theme_light() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
    #+
#scale_x_discrete(labels = c("Developed (open)", "Developed (other)", "Natural", "Crops","Other","Step length"))
#p1
#ggsave("img/fig_all_animals.pdf", width = 24, height = 12, units = "cm")
#ggsave("fig_all_animals_parameters_luis.pdf", width = 24, height = 12, units = "cm")
#ggsave("Graphs/Multi bird parameters.jpg")



#Make a density plot of the parameters
data %>%
  mutate(term=if_else(term=="forest27_endforest","Habitat selection",term),
         term=if_else(term=="log_sl_","Log step length",term),
         term=if_else(term=="ta_","Turning angle",term),
         term=if_else(term=="forest27_endforest:log_sl_","Log step length by habitat",term),
         term=if_else(term=="forest27_endforest:ta_","Turning angle by habitat",term)) %>% 
  ggplot(aes(x=estimate)) + 
  geom_histogram(aes(y=..density..),colour="black", fill="white") +
  geom_density(alpha=.2, fill="#FF6666") +
  facet_wrap(~term,scales="free")
  
```


Run replicate simulations:

```{r}

source("SSF simulation functions all birds.R")

num.sim.points.per.patch<-3
num.sim.per.point<-1


results.simulations <- split(condensed.dataframe.subset$id,condensed.dataframe.subset$id)

#for (i in 1:nrow(parameters.simulations)){
for (i in c(1,2)){

  

simulate.movement(focal.patch=focal.patch.database[[i]]$focal.patch.label,
                  tot.num.minutes=30,
                  fix.rate=5,
                  parameters.simulations=parameters.simulations,
                  num.sim.points.per.patch=num.sim.points.per.patch, #I tried to only put a number and then save the number I put with the name of the variable but I could not do it, so that is why I specifya outside the function the value and store in in the variable
                  num.sim.per.point=num.sim.per.point, #I tried to only put a number and then save the number I put with the name of the variable but I could not do it, so that is why I specifya outside the function the value and store in in the variable
                  map.full=land_use_raster,
                  map.cropped=forest.raster.cropped[[i]]$forest.raster.cropped,
                  map.cropped.labeled=forest.raster.cropped[[i]]$forest.raster.cropped.labeled,
                  name.output.dataframe=raw.results.emigration)
  
  results.simulations[[i]] <- raw.results.emigration
  
  
}
```




